CF Registry Analysis

### 2023-05-26 Christine Chan/CF Registry/cf_registry_analysis.qmd
Update cf_registry_analysis.qmd

annual <- read.csv("/Users/timvigers/Documents/Work/Christine Chan/CF registry data/CFF19_Annualized_Del1.csv",
                   na.strings = c("", "N/A")

@@

@@

@@

  yn_vars = c("A_IsOnEnzymes","A_corticosteroids1",

@@

                                "Age_YrEnd","A_weight","bmi", "age_perc"))]

>>>>

annual <- read.csv("/Users/timvigers/Documents/Work/Christine Chan/CF registry data/CFF19_Annualized_Del1.csv",na.strings = c("", "N/A")

@@

           A_supplement_feeding,A_feeding2,

@@

  # If A_supplement_feeding is 0, then A_feeding2 is also 0 because they are not 
  # on any supplemental feeding
  df$A_feeding2[df$A_supplement_feeding == 0] = 0

@@

  yn_vars = c("A_IsOnEnzymes","A_corticosteroids1","A_feeding2",

@@

                                "Age_YrEnd","A_weight","bmi", "age_perc",
                                "A_supplement_feeding"))]
